---
title: "linear model from Web"
author: "Cienna Baker-Salgado"
date: "Fall 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

On the scatterplot, it shows that SIMS is higher when the ARM strength starts to increase.

### Numerical results

The correlation is positive, ARM strength increase means that SIMS increases as well. 

### Inferential  (Build model.1)

summary.lm(model.1) 

#### Predict at target point

targtPoint = data.frame(GRIP=94, ARM=88)

#### scatterplot with model fit
  
plot(SIMS~ARM,data=data)

## Model 2 SIM~GRIP

### Now add in scatterplot

plot(SIMS~GRIP,data=data)

### Numerical results 

There is a positive correlation between the increase of both GRIP and SIMS

### Inferential  (Build model.2)

summary.lm(model.2)  

#### predict model.2 at target point

targtPoint = data.frame(grip=94, ARM=88)

#### now add the model fit to our plot for model.2
  
plot(SIMS~GRIP,data=data)

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

These results show the correlation between grip and strength and the simulation. The correlation between stimulation and grip strength is about 0.64 while arm and simulation strength is 0.69. Both are positive correlations.`
  
### Inferential  (Build 2-dimentional model.3)

summary.lm(model.3)

#### predict model.3 at target point
  
predict(model.3, TargtPoint, interval-'prediction')
The SIMS score predicted is 0.15, the interval prediction is -2.13 and 2.43.

## Comparing nested models ANOVA Test

anova(model.1, model.3) , anova(model.2, model.3)

### Model.1 vs Model.3

The model shows that there is a difference between the two due to the P-value being less than 0.05.

### Model.2 vs Model.3

There is a difference between model.2 and model.3  as the P-value is lower than 0.05.

## Informally compare Model.1 with model.2

Model.1 (SIMS~ARM) is best in comparison to model.2 (SIMS~GRIP) because model.1's residual was lower than model.2. 
